### 2017-04-08 chapters/04-results.tex
move temp to out directory

\section{Day In The Life Testing}

@@

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Data Rate (\SI{}{Bps}),
mark size=1.0pt,
mark repeat={5},
legend style ={
    at={(0.98,0.95)}, 
    anchor=north east, draw=black, 
    fill=white,align=left
}
]
\addplot+ table [
x=MET, y=error rate, col sep=comma
] {data/test-ditl/fcore.log.rxstats.csv};

\addplot+ table [
x=MET, y=bandwidth, col sep=comma
] {data/test-ditl/fcore.log.rxstats.csv};

\legend{Erroneous, Total}
\end{axis}
\end{tikzpicture}
\centering
\caption{DITL Test - Average data rates}
\label{fig:ditl-bandwidth}
\end{figure}

%
%
% \begin{figure}[H]
% \begin{tikzpicture}
% \begin{axis} [
% xlabel=Mission Elapsed Time (\SI{}{\second}),
% ylabel=Received Data (\SI{}{B}),
% mark size=1.0pt,
% mark repeat={5},
% legend style ={
%     at={(0.02,0.95)},
%     anchor=north west, draw=black,
%     fill=white,align=left
% }
% ]
% \addplot+ table [
% x=MET, y=received, col sep=comma
% ] {data/test-ditl/fcore.log.rxstats.csv};
%
% \addplot+ table [
% x=MET, y=valid, col sep=comma
% ] {data/test-ditl/fcore.log.rxstats.csv};
%
% \addplot+ table [
% x=MET, y=invalid, col sep=comma
% ] {data/test-ditl/fcore.log.rxstats.csv};
%
% \legend{Total, Valid Frame Data, Invalid Frame Data}
% \end{axis}
% \end{tikzpicture}
% \centering
% \caption{DITL Test - Received data}
% \label{fig:ditl-rxstats}
% \end{figure}

@@

\section{Radio Stress-Testing}

@@

\legend{Total, Erroneous, Fixed}
\end{axis}
\end{tikzpicture}
\centering
\caption{$\frac{8}{256}$ Error Test - Received Data}
\label{fig:stress-8.256}
\end{figure}

@@

\legend{Total, Erroneous, Fixed}
\end{axis}
\end{tikzpicture}
\centering
\caption{$\frac{14}{256}$ Error Test - Received Data}
\label{fig:stress-14.256}
\end{figure}

@@

@@

\legend{Total, Erroneous, Fixed}
\end{axis}
\end{tikzpicture}
\centering
\caption{$\frac{18}{256}$ Error Test - Received Data}
\label{fig:stress-18.256}
\end{figure}

>>>>

\section{Integrated Testing}

\subsection{Day In The Life Testing}

@@

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
mark repeat={5},
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]

\addplot+ table [
x=MET, y=received, col sep=comma
] {data/test-ditl/fcore.log.rxstats.csv};

\addplot+ table [
x=MET, y=invalid, col sep=comma
] {data/test-ditl/fcore.log.rxstats.csv};

\legend{Total, Erroneous}
\end{axis}
\end{tikzpicture}
\centering
\caption{DITL Test - Received frame data}
\label{fig:ditl-bandwidth}
\end{figure}

@@

\subsection{Radio Stress-Testing}

@@

\legend{Total, Erroneous}
\end{axis}
\end{tikzpicture}
\centering
\caption{$\frac{8}{256}$ Error Test - Received Data}
\label{fig:stress-8.256}
\end{figure}

@@

\legend{Total, Erroneous}
\end{axis}
\end{tikzpicture}
\centering
\caption{$\frac{14}{256}$ Error Test - Received Data}
\label{fig:stress-14.256}
\end{figure}

@@

\legend{Total, Erroneous}
\end{axis}
\end{tikzpicture}
\centering
\caption{$\frac{18}{256}$ Error Test - Received Data}
\label{fig:stress-18.256}
\end{figure}

Figure \ref{fig:stress-fec} shows that in all three tests, the amount of bytes
that were corrected using the frames' \acrlong{ecc} was similar. As expected,
the test with the highest byte error rate shows a slightly inferior correction
rate – frames that contain more than 16 erroneous bytes cannot be corrected at
all. Table \ref{tab:stress-fec} shows that the actual error correction rates
are close to the theoretical byte error rates induced at transmission as long
as the those theoretical rates are below the theoretical maximum.

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Error-Corrected Data (\SI{}{\byte}),
mark size=1.0pt,
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]

@@

\legend{$\frac{8}{256}$, $\frac{14}{256}$, $\frac{18}{256}$}
\end{axis}
\end{tikzpicture}
\centering
\caption{$\frac{14}{256}$ Error Tests - Error Correction Performance}
\label{fig:stress-fec}
\end{figure}
